---
title: "R Notebook"
output:
  word_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

libraries and custom functions

```{r}
library(mice)
library(pander)
library(xtable)
library(dplyr)
library(gt)
library(glue)
library(tidyverse)
library(flextable)
library(miceadds)
library(swfscMisc)
library(imputools)
library(haven)
library(sjmisc)
library(Hmisc)
library(psych)
library(lavaan)

#this will take a float (e.g. a p value) and return a string with 3 digits and no leading 0

bv <- function(val) {
  return(sub("^(-?)0.", "\\1.", sprintf("%.2f", val)))
}

#if the number is less than .001, it will give <.001. 
pv1 <- function(val) {
  return(paste("=", sub("^(-?)0.", "\\1.", sprintf("%.3f", val))))
}



```



#load in datasets for each cohort 

```{r}
load("~/Documents/PhD/MCS DATASETS/SES_inequalities_language/inequalities-language-ability/Datasets/2021-03-03_mcs_ses_comparison_WHITE/2021-03-03_mcs_ses_comparison_WHITE.Rdata")
mcs_imputation = mi.res

load("~/Documents/PhD/MCS DATASETS/SES_inequalities_language/inequalities-language-ability/Datasets/2021-03-03_bcs_ses_WHITEsample/2021-03-03_bcs_ses_WHITEsample.Rdata")
bcs_imputation = mi.res
```


regression models. want one for each age (early childhood, late childhood, adolescence) for occupational status and for education, in both cohorts. 
confounders only models for R2 table later. we are not controlling for ethnicity in these models because we are only looking at white ethnicity. 

```{r}
#regression models####

#MCS2001 regressions 

#age 5
mcs_age5_occupation <- with(mcs_imputation, lm(standardised_vocab5 ~ gender +  EAL + standardised_age5+  occupational_status, weights = weight)) 
mcs_age5_education <- with(mcs_imputation, lm(standardised_vocab5 ~ gender +  EAL + standardised_age5+ highest_household_education, weights = weight))
mcs_age5_confounders<- with(mcs_imputation, lm(standardised_vocab5 ~ gender +  EAL + standardised_age5, weights = weight))
#age 11
mcs_age11_occupation <- with(mcs_imputation, lm(standardised_vocab11 ~ gender +  EAL + standardised_age11+  occupational_status, weights = weight)) 
mcs_age11_education <- with(mcs_imputation, lm(standardised_vocab11 ~ gender +  EAL + standardised_age11+ highest_household_education, weights = weight))
mcs_age11_confounders<- with(mcs_imputation, lm(standardised_vocab11 ~ gender +  EAL + standardised_age11,weights = weight))
#age 14
mcs_age14_occupation <- with(mcs_imputation, lm(standardised_vocab14 ~ gender +  EAL + standardised_age14+  occupational_status,weights = weight)) 
mcs_age14_education <- with(mcs_imputation, lm(standardised_vocab14 ~ gender +  EAL + standardised_age14+ highest_household_education,weights = weight))
mcs_age14_confounders<- with(mcs_imputation, lm(standardised_vocab14 ~ gender +  EAL + standardised_age14,weights = weight))

#BCS1970 regressions 
bcs_age5_occupation <- with(bcs_imputation, lm(standardised_vocab5 ~ gender +  EAL + standardised_age5+  occupational_status,weights = weight)) 
bcs_age5_education <- with(bcs_imputation, lm(standardised_vocab5 ~ gender +  EAL + standardised_age5+ highest_household_education,weights = weight))
bcs_age5_confounders<- with(bcs_imputation, lm(standardised_vocab5 ~ gender +  EAL + standardised_age5, weights = weight))
#age 10
bcs_age10_occupation <- with(bcs_imputation, lm(standardised_vocab10 ~ gender +  EAL + standardised_age10+  occupational_status, weights = weight)) 
bcs_age10_education <- with(bcs_imputation, lm(standardised_vocab10 ~ gender +  EAL + standardised_age10+ highest_household_education, weights = weight))
bcs_age10_confounders<- with(bcs_imputation, lm(standardised_vocab10 ~ gender +  EAL + standardised_age10, weights = weight))
#age 16
bcs_age16_occupation <- with(bcs_imputation, lm(standardised_vocab16 ~ gender +  EAL + standardised_age16+  occupational_status, weights = weight)) 
bcs_age16_education <- with(bcs_imputation, lm(standardised_vocab16 ~ gender +  EAL + standardised_age16+ highest_household_education, weights = weight))
bcs_age16_confounders<- with(bcs_imputation, lm(standardised_vocab16 ~ gender +  EAL + standardised_age16, weights = weight))

```

get the coefficients for the SES measures. 


```{r}
mcs_age5_occupation_results = round(summary(pool(mcs_age5_occupation), conf.int =TRUE),2)
mcs_age5_education_results = round(summary(pool(mcs_age5_education), conf.int =TRUE),2)
mcs_age11_occupation_results = round(summary(pool(mcs_age11_occupation), conf.int =TRUE),2)
mcs_age11_education_results = round(summary(pool(mcs_age11_education), conf.int =TRUE),2)
mcs_age14_occupation_results = round(summary(pool(mcs_age14_occupation), conf.int =TRUE),2)
mcs_age14_education_results = round(summary(pool(mcs_age14_education), conf.int =TRUE),2)


bcs_age5_occupation_results = round(summary(pool(bcs_age5_occupation), conf.int =TRUE),2)
bcs_age5_education_results = round(summary(pool(bcs_age5_education), conf.int =TRUE),2)
bcs_age10_occupation_results = round(summary(pool(bcs_age10_occupation), conf.int =TRUE),2)
bcs_age10_education_results = round(summary(pool(bcs_age10_education), conf.int =TRUE),2)
bcs_age16_occupation_results = round(summary(pool(bcs_age16_occupation), conf.int =TRUE),2)
bcs_age16_education_results = round(summary(pool(bcs_age16_education), conf.int =TRUE),2)


#pull out SES coefficients for table

MCS_age5_occupation_results = mcs_age5_occupation_results[5:7,]
MCS_age5_education_results = mcs_age5_education_results[5:7,]
MCS_age11_occupation_results = mcs_age11_occupation_results[5:7,]
MCS_age11_education_results = mcs_age11_education_results[5:7,]
MCS_age14_occupation_results = mcs_age14_occupation_results[5:7,]
MCS_age14_education_results = mcs_age14_education_results[5:7,]

BCS_age5_occupation_results = bcs_age5_occupation_results[5:7,]
BCS_age5_education_results = bcs_age5_education_results[5:7,]
BCS_age10_occupation_results = bcs_age10_occupation_results[5:7,]
BCS_age10_education_results = bcs_age10_education_results[5:7,]
BCS_age16_occupation_results = bcs_age16_occupation_results[5:7,]
BCS_age16_education_results = bcs_age16_education_results[5:7,]

MCS_age5_results = rbind(MCS_age5_occupation_results, MCS_age5_education_results)
MCS_age11_results = rbind(MCS_age11_occupation_results, MCS_age11_education_results)
MCS_age14_results = rbind(MCS_age14_occupation_results, MCS_age14_education_results)
BCS_age5_results = rbind(BCS_age5_occupation_results, BCS_age5_education_results)
BCS_age10_results = rbind(BCS_age10_occupation_results, BCS_age10_education_results)
BCS_age16_results = rbind(BCS_age16_occupation_results, BCS_age16_education_results)




```

prepare data for tables
```{r}

MCS_age5_results$estimate = bv(MCS_age5_results$estimate) #no leading 0 
#MCS_age5_results$estimate = round(MCS_age5_results$estimate,2)
MCS_age5_results$`2.5 %` = bv(MCS_age5_results$`2.5 %`)
MCS_age5_results$`97.5 %` = bv(MCS_age5_results$`97.5 %`)
MCS_age5_results$p.value1= ifelse(MCS_age5_results$p.value< .001, "<.001" , pv1(MCS_age5_results$p.value))
#MCS_age5_results$p.value = round(MCS_age5_results$p.value, 3)
MCS_age5_results$coefficient = paste0(MCS_age5_results$estimate, "[", MCS_age5_results$`2.5 %`, ";", MCS_age5_results$`97.5 %`, "]")
#MCS_age5_results$p.value [MCS_age5_results$p.value <.001] <- paste0("<.001") #change p=0.000 to p<.001
MCS_age5_results$stars = add.significance.stars(MCS_age5_results$p.value, cutoffs=c(0.05, 0.01, 0.001))
MCS_age5_results$p1 = paste0(MCS_age5_results$p.value1, "")
MCS_age5_results$p = paste0("p", MCS_age5_results$p1)
MCS_age5_results$new_coef = paste0(MCS_age5_results$coefficient, MCS_age5_results$stars)  #combine coefficients and stars into column.


MCS_age11_results$estimate = bv(MCS_age11_results$estimate) #no leading 0 
#MCS_age11_results$estimate = round(MCS_age11_results$estimate,2)
MCS_age11_results$`2.5 %` = bv(MCS_age11_results$`2.5 %`)
MCS_age11_results$`97.5 %` = bv(MCS_age11_results$`97.5 %`)
MCS_age11_results$p.value1= ifelse(MCS_age11_results$p.value< .001, "<.001" , pv1(MCS_age11_results$p.value))
#MCS_age11_results$p.value = round(MCS_age11_results$p.value, 3)
MCS_age11_results$coefficient = paste0(MCS_age11_results$estimate, "[", MCS_age11_results$`2.5 %`, ";", MCS_age11_results$`97.5 %`, "]")
#MCS_age11_results$p.value [MCS_age11_results$p.value <.001] <- paste0("<.001") #change p=0.000 to p<.001
MCS_age11_results$stars = add.significance.stars(MCS_age11_results$p.value, cutoffs=c(0.05, 0.01, 0.001))
MCS_age11_results$p1 = paste0(MCS_age11_results$p.value1, "")
MCS_age11_results$p = paste0("p", MCS_age11_results$p1)
MCS_age11_results$new_coef = paste0(MCS_age11_results$coefficient, MCS_age11_results$stars)  #combine coefficients and stars into column.


MCS_age14_results$estimate = bv(MCS_age14_results$estimate) #no leading 0 
#MCS_age14_results$estimate = round(MCS_age14_results$estimate,2)
MCS_age14_results$`2.5 %` = bv(MCS_age14_results$`2.5 %`)
MCS_age14_results$`97.5 %` = bv(MCS_age14_results$`97.5 %`)
MCS_age14_results$p.value1= ifelse(MCS_age14_results$p.value< .001, "<.001" , pv1(MCS_age14_results$p.value))
#MCS_age14_results$p.value = round(MCS_age14_results$p.value, 3)
MCS_age14_results$coefficient = paste0(MCS_age14_results$estimate, "[", MCS_age14_results$`2.5 %`, ";", MCS_age14_results$`97.5 %`, "]")
#MCS_age14_results$p.value [MCS_age14_results$p.value <.001] <- paste0("<.001") #change p=0.000 to p<.001
MCS_age14_results$stars = add.significance.stars(MCS_age14_results$p.value, cutoffs=c(0.05, 0.01, 0.001))
MCS_age14_results$p1 = paste0(MCS_age14_results$p.value1, "")
MCS_age14_results$p = paste0("p", MCS_age14_results$p1)
MCS_age14_results$new_coef = paste0(MCS_age14_results$coefficient, MCS_age14_results$stars)  #combine coefficients and stars into column.

BCS_age5_results$estimate = bv(BCS_age5_results$estimate) #no leading 0 
#BCS_age5_results$estimate = round(BCS_age5_results$estimate,2)
BCS_age5_results$`2.5 %` = bv(BCS_age5_results$`2.5 %`)
BCS_age5_results$`97.5 %` = bv(BCS_age5_results$`97.5 %`)
BCS_age5_results$p.value1= ifelse(BCS_age5_results$p.value< .001, "<.001" , pv1(BCS_age5_results$p.value))
#BCS_age5_results$p.value = round(BCS_age5_results$p.value, 3)
BCS_age5_results$coefficient = paste0(BCS_age5_results$estimate, "[", BCS_age5_results$`2.5 %`, ";", BCS_age5_results$`97.5 %`, "]")
#BCS_age5_results$p.value [BCS_age5_results$p.value <.001] <- paste0("<.001") #change p=0.000 to p<.001
BCS_age5_results$stars = add.significance.stars(BCS_age5_results$p.value, cutoffs=c(0.05, 0.01, 0.001))
BCS_age5_results$p1 = paste0(BCS_age5_results$p.value1, "")
BCS_age5_results$p = paste0("p", BCS_age5_results$p1)
BCS_age5_results$new_coef = paste0(BCS_age5_results$coefficient, BCS_age5_results$stars)  #combine coefficients and stars into column.


BCS_age10_results$estimate = bv(BCS_age10_results$estimate) #no leading 0 
#BCS_age10_results$estimate = round(BCS_age10_results$estimate,2)
BCS_age10_results$`2.5 %` = bv(BCS_age10_results$`2.5 %`)
BCS_age10_results$`97.5 %` = bv(BCS_age10_results$`97.5 %`)
BCS_age10_results$p.value1= ifelse(BCS_age10_results$p.value< .001, "<.001" , pv1(BCS_age10_results$p.value))
#BCS_age10_results$p.value = round(BCS_age10_results$p.value, 3)
BCS_age10_results$coefficient = paste0(BCS_age10_results$estimate, "[", BCS_age10_results$`2.5 %`, ";", BCS_age10_results$`97.5 %`, "]")
#BCS_age10_results$p.value [BCS_age10_results$p.value <.001] <- paste0("<.001") #change p=0.000 to p<.001
BCS_age10_results$stars = add.significance.stars(BCS_age10_results$p.value, cutoffs=c(0.05, 0.01, 0.001))
BCS_age10_results$p1 = paste0(BCS_age10_results$p.value1, "")
BCS_age10_results$p = paste0("p", BCS_age10_results$p1)
BCS_age10_results$new_coef = paste0(BCS_age10_results$coefficient, BCS_age10_results$stars)  #combine coefficients and stars into column.

BCS_age16_results$estimate = bv(BCS_age16_results$estimate) #no leading 0 
#BCS_age16_results$estimate = round(BCS_age16_results$estimate,2)
BCS_age16_results$`2.5 %` = bv(BCS_age16_results$`2.5 %`)
BCS_age16_results$`97.5 %` = bv(BCS_age16_results$`97.5 %`)
BCS_age16_results$p.value1= ifelse(BCS_age16_results$p.value< .001, "<.001" , pv1(BCS_age16_results$p.value))
#BCS_age16_results$p.value = round(BCS_age16_results$p.value, 3)
BCS_age16_results$coefficient = paste0(BCS_age16_results$estimate, "[", BCS_age16_results$`2.5 %`, ";", BCS_age16_results$`97.5 %`, "]")
#BCS_age16_results$p.value [BCS_age16_results$p.value <.001] <- paste0("<.001") #change p=0.000 to p<.001
BCS_age16_results$stars = add.significance.stars(BCS_age16_results$p.value, cutoffs=c(0.05, 0.01, 0.001))
BCS_age16_results$p1 = paste0(BCS_age16_results$p.value1, "")
BCS_age16_results$p = paste0("p", BCS_age16_results$p1)
BCS_age16_results$new_coef = paste0(BCS_age16_results$coefficient, BCS_age16_results$stars)  #combine coefficients and stars into column.

MCS_age5_tableData <- MCS_age5_results %>% 
  select(term, new_coef, p) 
  names(MCS_age5_tableData) =c("term", "MCS_coef5", "MCS_p5")

MCS_age11_tableData <- MCS_age11_results %>% 
  select(term, new_coef, p)
names(MCS_age11_tableData) =c("term", "MCS_coef11", "MCS_p11")

MCS_age14_tableData <- MCS_age14_results %>% 
  select(term, new_coef, p)
names(MCS_age14_tableData) =c("term", "MCS_coef14", "MCS_p14")

BCS_age5_tableData <- BCS_age5_results %>% 
  select(term, new_coef, p)
names(BCS_age5_tableData) =c("term", "BCS_coef5", "BCS_p5")

BCS_age10_tableData <- BCS_age10_results %>% 
  select(term, new_coef, p)
names(BCS_age10_tableData) =c("term", "BCS_coef10", "BCS_p10")

BCS_age16_tableData <- BCS_age16_results %>% 
  select(term, new_coef, p)
names(BCS_age16_tableData) =c("term", "BCS_coef16", "BCS_p16")


BCS_data <- merge(all=TRUE, BCS_age5_tableData, BCS_age10_tableData, by="term")
BCS_data <- merge(all=TRUE, BCS_data, BCS_age16_tableData, by="term")

MCS_data <- merge(all=TRUE, MCS_age5_tableData, MCS_age11_tableData, by="term")
MCS_data <- merge(all=TRUE, MCS_data,MCS_age14_tableData, by="term")


BCS_data$early_childhood_bcs = paste0(BCS_data$BCS_coef5,"\n", BCS_data$BCS_p5)
BCS_data$late_childhood_bcs = paste0(BCS_data$BCS_coef10,"\n", BCS_data$BCS_p10)
BCS_data$adolescence_bcs = paste0(BCS_data$BCS_coef16,"\n", BCS_data$BCS_p16)

MCS_data$early_childhood_mcs = paste0(MCS_data$MCS_coef5,"\n", MCS_data$MCS_p5)
MCS_data$late_childhood_mcs = paste0(MCS_data$MCS_coef11,"\n", MCS_data$MCS_p11)
MCS_data$adolescence_mcs = paste0(MCS_data$MCS_coef14,"\n", MCS_data$MCS_p14)



BCS = BCS_data %>% 
  select (term, early_childhood_bcs, late_childhood_bcs, adolescence_bcs)

MCS = MCS_data %>% 
  select (term, early_childhood_mcs, late_childhood_mcs, adolescence_mcs)




cross_cohort_data = cbind(BCS, MCS)

names(cross_cohort_data) = c("Indicator","early_childhood_bcs" ,"late_childhood_bcs","adolescent_bcs","term" ,"early_childhood_mcs",  "late_childhood_mcs", "adolescent_mcs")


cross_cohort_data <- cross_cohort_data %>% 
  select(Indicator, early_childhood_bcs,  late_childhood_bcs, adolescent_bcs, early_childhood_mcs, late_childhood_mcs, adolescent_mcs)

#add in reference categories 
cross_cohort_data = cross_cohort_data  %>% add_row(Indicator= "highest_household_education1",  .before=1) %>% 
  add_row(Indicator= "occupational_status2",  .before=5) 
cross_cohort_data[is.na(cross_cohort_data)] <- "REFERENCE"

#add indicator labels for vertical column in table. space for most of these as will merge cells later. 
cross_cohort_data = cross_cohort_data %>%  add_column(z= c("Parent Education", "  ", "  ", "  ", 
                                                     
                                                     "Occupational Status",  "  ", "  ", "  "
                                                    ),.before = 1)


#rename SES variables
cross_cohort_data$Indicator <- c("No/low level \n qualifications", "O levels/ GCSEs  \n grades A*-C", "Post 16 education", "University level \n qualifications", 
                            "Routine", "Unemployed", "Intermediate", "Higher managerial ")

cross_cohort_data[is.na(cross_cohort_data)] <- "   "
```


#create table with flextable package, which can be exported to word 

```{r}
library(officer)

#define border
my_border = border= fp_border(color="black", width=1)
cross_cohort_flex <- cross_cohort_data %>% 
  flextable() %>% 
  font(fontname = "Times New Roman", part="all") %>% 
  fontsize(size=9, part = "all") %>% 
  align(j=2, align="left", part="all") %>% 
  align(j=3:8, align="center", part="all") %>% 
  color(j=1:8, color="black", part="all") %>% 
  width(j=1, width=0.3) %>% 
  width(j=2, width=0.8) %>% 
  width(j=3:8, width=1.1) %>% 
  line_spacing(j=3:8, space=1.5) %>% 
  line_spacing(j=1, space=1.5) %>% 
  border_remove() %>% 
  hline_top(j=1:8, part="all", border=my_border) %>% 
  hline_bottom(j=1:8,part="body",  border=my_border) %>% 
  set_header_labels(z= " ", Inidcator= "Indicator",early_childhood_bcs= "Early Childhood Vocabulary (BCS)", late_childhood_bcs="Late Childhood Vocabulary (BCS)",
                    adolescent_bcs = "Adolescent Vocabulary (BCS)",
                    early_childhood_mcs ="Early Childhood Vocabulary (MCS)", late_childhood_mcs="Late Childhood Vocabulary (MCS)", 
                    adolescent_mcs = "Adolescent Vocabulary (MCS)") %>% 
  merge_at(j=1, i = 1:4) %>% 
  merge_at(j=1, i=5:8) %>% 
  rotate(i=1:4, j=1, rotation="btlr", align="center") %>% 
  rotate(i=5:8, j=1, rotation="btlr", align="center") %>% 
 print( preview = "docx") 



 
```



r squared values

```{r}
#MCS2001
mcs_age5_occupation_r2 = round(pool.r.squared(mcs_age5_occupation),4)*100
mcs_age11_occupation_r2 = round(pool.r.squared(mcs_age11_occupation),4)*100
mcs_age14_occupation_r2 = round(pool.r.squared(mcs_age14_occupation),4)*100

mcs_age5_education_r2 = round(pool.r.squared(mcs_age5_education),4)*100
mcs_age11_education_r2= round(pool.r.squared(mcs_age11_education),4)*100
mcs_age14_education_r2 = round(pool.r.squared(mcs_age14_education),4)*100

mcs_age5_confounders_r2 = round(pool.r.squared(mcs_age5_confounders), 4)*100
mcs_age11_confounders_r2= round(pool.r.squared(mcs_age11_confounders), 4)*100
mcs_age14_confounders_r2= round(pool.r.squared(mcs_age14_confounders), 4)*100

#partial r squared
mcs_age5_occupation_partial = mcs_age5_occupation_r2 - mcs_age5_confounders_r2
mcs_age5_education_partial = mcs_age5_education_r2 - mcs_age5_confounders_r2
mcs_age11_occupation_partial = mcs_age11_occupation_r2 - mcs_age11_confounders_r2
mcs_age11_education_partial = mcs_age11_education_r2 - mcs_age11_confounders_r2
mcs_age14_occupation_partial = mcs_age14_occupation_r2 - mcs_age14_confounders_r2
mcs_age14_education_partial = mcs_age14_education_r2 - mcs_age14_confounders_r2

#BCS1970
bcs_age5_occupation_r2 = round(pool.r.squared(bcs_age5_occupation),4)*100
bcs_age10_occupation_r2 = round(pool.r.squared(bcs_age10_occupation),4)*100
bcs_age16_occupation_r2 = round(pool.r.squared(bcs_age16_occupation),4)*100

bcs_age5_education_r2 = round(pool.r.squared(bcs_age5_education),4)*100
bcs_age10_education_r2= round(pool.r.squared(bcs_age10_education),4)*100
bcs_age16_education_r2 = round(pool.r.squared(bcs_age16_education),4)*100

bcs_age5_confounders_r2 = round(pool.r.squared(bcs_age5_confounders), 4)*100
bcs_age10_confounders_r2= round(pool.r.squared(bcs_age10_confounders), 4)*100
bcs_age16_confounders_r2= round(pool.r.squared(bcs_age16_confounders), 4)*100

#partial r squared
bcs_age5_occupation_partial = bcs_age5_occupation_r2 - bcs_age5_confounders_r2
bcs_age5_education_partial= bcs_age5_education_r2 - bcs_age5_confounders_r2
bcs_age10_occupation_partial = bcs_age10_occupation_r2 - bcs_age10_confounders_r2
bcs_age10_education_partial = bcs_age10_education_r2 - bcs_age10_confounders_r2
bcs_age16_occupation_partial= bcs_age16_occupation_r2 - bcs_age16_confounders_r2
bcs_age16_education_partial= bcs_age16_education_r2 - bcs_age16_confounders_r2


bcs_partial = as.data.frame(rbind(bcs_age5_education_partial,  bcs_age10_education_partial, bcs_age16_education_partial, bcs_age5_occupation_partial, bcs_age10_occupation_partial, bcs_age16_occupation_partial))
mcs_partial = as.data.frame(rbind(mcs_age5_education_partial,  mcs_age11_education_partial, mcs_age14_education_partial, mcs_age5_occupation_partial, mcs_age11_occupation_partial, mcs_age14_occupation_partial))


bcs_partial = bcs_partial %>%  add_column(indicator= c("Parent Education (early bcs)", "Parent education(late bcs)", "parent education (adolescent bcs)", "Occupation (early bcs)", "occupation (late bcs)", "occupation(adolescent bcs)"), .before = 1)
mcs_partial = mcs_partial %>%  add_column(indicator= c("Parent Education (early mcs)", "Parent education(late mcs)", "parent education (adolescent mcs)", "Occupation (early mcs)", "occupation (late mcs)", "occupation(adolescent mcs)"), .before = 1)

bcs_partial = bcs_partial[,1:2]
mcs_partial = mcs_partial[,1:2]

partial_r2_values = cbind(bcs_partial, mcs_partial)
rownames(partial_r2_values) <- NULL


```

