---
title: "R Notebook"
output:
  word_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

Descriptive statistics for imputed data. first of all load in packages and custom functions. 
custom functions require imputed data to be in long format without the observed data included. 

```{r}
library(mice)
library(pander)
library(xtable)
library(dplyr)
library(gt)
library(glue)
library(miceadds)
library(swfscMisc)
library(imputools)
library(haven)
library(sjmisc)
library(Hmisc)
library(psych)
library(lavaan)
library(ggplot2)
library(ggpubr)
library(officer)
library(flextable)
library(ftExtra)
library(dummies)
library(tidyverse)
weighted_descriptives_imputed_datasets<- function (dataAll,variable) {
  variable=deparse(substitute(variable))
  imputed_datasets <- unique(dataAll$.imp)
  results <- data.frame(
    Mean = as.numeric(rep(0, length(imputed_datasets))),
    SD = as.numeric(rep(0, length(imputed_datasets))),
    lower=as.numeric(rep(0, length(imputed_datasets))),
    upper=as.numeric(rep(0, length(imputed_datasets))))
  results$Imputed <-  imputed_datasets
  for (i in 1:length(imputed_datasets)) {
    data <- dataAll[dataAll$.imp == imputed_datasets[i], ]
    results[i, "Mean"] <- get_weighted_descriptives(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[1]
    results[i, "SD"] <- get_weighted_descriptives(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[2]
    results[i, "lower"] <- get_weighted_descriptives(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[3]
    results[i, "upper"] <- get_weighted_descriptives(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[4]
  }
  return (results)
}
weighted_proportions_imputed_datasets<- function (dataAll,variable) {
  variable=deparse(substitute(variable))
  imputed_datasets <- unique(dataAll$.imp)
  results <- data.frame(
    Level1 = as.numeric(rep(0, length(imputed_datasets))),
    Level2 = as.numeric(rep(0, length(imputed_datasets))),
    Level3=as.numeric(rep(0, length(imputed_datasets))),
    Level4=as.numeric(rep(0, length(imputed_datasets))),
    Level5=as.numeric(rep(0, length(imputed_datasets))),
    Level6=as.numeric(rep(0, length(imputed_datasets))),
    Level7=as.numeric(rep(0, length(imputed_datasets))),
    Level8=as.numeric(rep(0, length(imputed_datasets))),
    Level9=as.numeric(rep(0, length(imputed_datasets))),
    Level10=as.numeric(rep(0, length(imputed_datasets))))
  results$Imputed <-  imputed_datasets
  for (i in 1:length(imputed_datasets)) {
    data <- dataAll[dataAll$.imp == imputed_datasets[i], ]
    results[i, "Level1"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[1]
    results[i, "Level2"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[2]
    results[i, "Level3"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[3]
    results[i, "Level4"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[4]
    results[i, "Level5"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[5]
    results[i, "Level6"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[6]
    results[i, "Level7"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[7]
    results[i, "Level8"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[8]
    results[i, "Level9"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[9]
    results[i, "Level10"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$mcs2_weight)[10]
    
  }
  return (results)
}

#Load in data

load("~/Documents/updated MCS datasets/inequalities datasets /2022-10-26_mcs_ses_imputedRQ1/2022-10-26_mcs_ses_imputedRQ1.Rdata")
imputed_mcs2=mi.res

#convert imputed data to long format without observed data
long_format_mcs <- mice::complete(imputed_mcs2, "long", include=FALSE)
#redorder nvq and occupational status to have same order as whole cohort data - for occupational status and nvq
long_format_mcs$highest_nvq = factor(long_format_mcs$highest_NVQ, levels = c("1", "2", "3", "4", "5", "0"))
long_format_mcs$occupational_status = factor(long_format_mcs$occupational_status, levels = c( "2", "3", "4", "1"))


```

run descritpives
```{r include = FALSE}
#numeric variables - means & SDs
#calculate descriptives across imputed datasets
vocab_age3Descriptives = weighted_descriptives_imputed_datasets(long_format_mcs, vocabulary_age3)
vocab_age5Descriptives = weighted_descriptives_imputed_datasets(long_format_mcs, vocabulary_age5)
vocab_age11Descriptives = weighted_descriptives_imputed_datasets(long_format_mcs, vocabulary_age11)
vocab_age14Descriptives = weighted_descriptives_imputed_datasets(long_format_mcs, vocabulary_age14)

#combine across imputed datasets
combined_vocab_age3Descriptives = round(combine_imputed_descriptives(vocab_age3Descriptives),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1) 

combined_vocab_age5Descriptives = round(combine_imputed_descriptives(vocab_age5Descriptives),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1) 

combined_vocab_age11Descriptives = round(combine_imputed_descriptives(vocab_age11Descriptives),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1) 

combined_vocab_age14Descriptives = round(combine_imputed_descriptives(vocab_age14Descriptives),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1) 

#categorical variables: proportions
sexProportions = weighted_proportions_imputed_datasets(long_format_mcs, gender) %>% 
  select(Level1:Level2) 
ethnicityProportions = weighted_proportions_imputed_datasets(long_format_mcs, ethnicity) %>% 
  select(Level1:Level6) 
ealProportions = weighted_proportions_imputed_datasets(long_format_mcs, language_used_at_home) %>% 
  select(Level1:Level3) 
nvqProportions = weighted_proportions_imputed_datasets(long_format_mcs, highest_NVQ) %>% 
  select(Level1:Level6) 
incomeProportions = weighted_proportions_imputed_datasets(long_format_mcs, income_quintiles) %>% 
  select(Level1:Level5) 
occupationProportions = weighted_proportions_imputed_datasets(long_format_mcs, occupational_status) %>% 
  select(Level1:Level4) 
wealthProportions = weighted_proportions_imputed_datasets(long_format_mcs, wealth_quintiles) %>% 
  select(Level1:Level5)  
imdProportions = weighted_proportions_imputed_datasets(long_format_mcs, imd) %>% 
  select(Level1:Level10)  

 
sexCombined = round(combine_imputed_descriptives(sexProportions)*100, 2) %>% 
  slice_head(n=1) %>% 
  rename("Sex (Male)" = Level1,
         "Sex (Female)" = Level2) 
sexCombined = as.data.frame(t(sexCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
ethnicityCombined = round(combine_imputed_descriptives(ethnicityProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename( "Ethnicity \n (White)" = Level1, 
          "Ethnicity \n (mixed)" = Level2,
          "Ethnicity \n (Indian)" = Level3, 
          "Ethnicity \n (Pakistani & Bangladeshi)" = Level4, 
          "Ethnicity \n (Black/ Black British)" = Level5, 
          "Ethnicity \n (other incl. Chinese)" = Level6)
ethnicityCombined = as.data.frame(t(ethnicityCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
ealCombined = round(combine_imputed_descriptives(ealProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("EAL \n (English only)" = Level1, 
         "EAL \n (English and another language)" = Level2,
         "EAL \n (only another language)" = Level3)
ealCombined = as.data.frame(t(ealCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
nvqCombined = round(combine_imputed_descriptives(nvqProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Parent Education \n (NVQ1)" = Level1, 
         "Parent Education \n (NVQ2)"= Level2, 
         "Parent Education \n (NVQ3)" = Level3,
         "Parent Education \n (NVQ4)" = Level4,
         "Parent Education \n (NVQ5)" = Level5,
         "Parent Education \n (None of these/overseas qualifications)" = Level6)
nvqCombined = as.data.frame(t(nvqCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
incomeCombined = round(combine_imputed_descriptives(incomeProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Income Quintile 1" = Level1, 
         "Income Quintile 2" = Level2, 
         "Income Quintile 3" = Level3, 
         "Income Quintile 4" = Level4 , 
         "Income Quintile 5" = Level5)
incomeCombined = as.data.frame(t(incomeCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
occupationCombined = round(combine_imputed_descriptives(occupationProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Occupational Status \n (routine)" = Level1, 
         "Occupational Status \n (intermediate)" = Level2,
         "Occupational Status \n (higher managerial)" = Level3,
         "Occupational Status \n (unemployed)" = Level4)
occupationCombined = as.data.frame(t(occupationCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
wealthCombined = round(combine_imputed_descriptives(wealthProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Wealth Quintile 1" = Level1, 
         "Wealth Quintile 2" = Level2, 
         "Wealth Quintile 3" = Level3, 
         "Wealth Quintile 4" = Level4, 
         "Wealth Quintile 5" = Level5)
wealthCombined = as.data.frame(t(wealthCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
imdCombined = round(combine_imputed_descriptives(imdProportions)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Relative Neighbourhood Deprivation \n (most deprived decile)" = Level1, 
         "Relative Neighbourhood Deprivation \n (10 - <20%)" = Level2, 
         "Relative Neighbourhood Deprivation \n (20 - <30%)" = Level3, 
         "Relative Neighbourhood Deprivation \n (30 - <40%)" = Level4, 
         "Relative Neighbourhood Deprivation \n (40 - <50%)" = Level5, 
         "Relative Neighbourhood Deprivation \n (50 - <60%)" = Level6, 
         "Relative Neighbourhood Deprivation \n (60 - <70%)" = Level7, 
         "Relative Neighbourhood Deprivation \n (70 - <80%)" = Level8, 
         "Relative Neighbourhood Deprivation \n (80 - <90%)"= Level9,
         "Relative Neighbourhood Deprivation \n (least deprived decile)" = Level10)
imdCombined = as.data.frame(t(imdCombined)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
```

prepare for table.
will need to paste in 95%CIs with means and SDs and then put everything into one dataframe
```{r}
vocabulary_age3Descriptives = combined_vocab_age3Descriptives %>% add_column(paste0(combined_vocab_age3Descriptives$Mean,"(±",combined_vocab_age3Descriptives$SD,")", "\n", "[", combined_vocab_age3Descriptives$lower, ";", combined_vocab_age3Descriptives$upper,"]")) %>% 
  rename("cmVocabAge3" = `paste0(...)`) %>% 
  add_column("Variable" = "Cohort Member Vocabulary \n Age 3 (Naming Vocabulary Score)") %>% 
  select(Variable, cmVocabAge3)  %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = cmVocabAge3) 


vocabulary_age5Descriptives = combined_vocab_age5Descriptives %>% add_column(paste0(combined_vocab_age5Descriptives$Mean,"(±",combined_vocab_age5Descriptives$SD,")", "\n", "[", combined_vocab_age5Descriptives$lower, ";", combined_vocab_age5Descriptives$upper,"]")) %>% 
  rename("cmVocabAge5" = `paste0(...)`) %>% 
  add_column("Variable" = "Cohort Member Vocabulary \n Age 5 (Naming Vocabulary Score)") %>% 
  select(Variable, cmVocabAge5)  %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = cmVocabAge5) 

vocabulary_age11Descriptives = combined_vocab_age11Descriptives %>% add_column(paste0(combined_vocab_age11Descriptives$Mean,"(±",combined_vocab_age11Descriptives$SD,")", "\n", "[", combined_vocab_age11Descriptives$lower, ";", combined_vocab_age11Descriptives$upper,"]")) %>% 
  rename("cmVocabAge11" = `paste0(...)`) %>% 
  add_column("Variable" = "Cohort Member Vocabulary \n Age 11 (Verbal Similarities Score)") %>% 
  select(Variable, cmVocabAge11)  %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = cmVocabAge11) 

vocabulary_age14Descriptives = combined_vocab_age14Descriptives %>% add_column(paste0(combined_vocab_age14Descriptives$Mean,"(±",combined_vocab_age14Descriptives$SD,")", "\n", "[", combined_vocab_age14Descriptives$lower, ";", combined_vocab_age14Descriptives$upper,"]")) %>% 
  rename("cmVocabAge14" = `paste0(...)`) %>% 
  add_column("Variable" = "Cohort Member Vocabulary \n Age 14 (Word Activity Test Score)") %>% 
  select(Variable, cmVocabAge14)  %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = cmVocabAge14) 

#put into one overall dataframe that can then  put into flex table
descriptivesTable = rbind(vocabulary_age3Descriptives, vocabulary_age5Descriptives,
                          vocabulary_age11Descriptives, vocabulary_age14Descriptives,
                          sexCombined, ethnicityCombined, ealCombined, 
                          nvqCombined, incomeCombined, wealthCombined, occupationCombined,
                          imdCombined) %>% 
  add_row(Variable = "Vocabulary", .before = 1) %>%  #add in rows to divide table up 
  add_row(Variable = "Demographics", .before = 6) %>% 
  add_row(Variable = "Socioeconomic Circumstances", .before = 18)
descriptivesTable [is.na(descriptivesTable )] <- " "

```

whole cohort descriptives , so can compare full cohort to analytic sample. 

```{r}
#read in full cohort data
mcs_cohort<-read.csv("SES_data.csv")
mcs_cohort[,1]<- NULL
#redorder nvq and occupational status variables 
mcs_cohort$highest_nvq = factor(mcs_cohort$highest_NVQ, levels = c("1", "2", "3", "4", "5", "0"))
mcs_cohort$occupational_status = factor(mcs_cohort$occupational_status, levels = c( "2", "3", "4", "1"))
#get weighted proportions - need to remove NA values 
#sex
cohort_sex = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$gender),]$gender,
                         mcs_cohort[!is.na(mcs_cohort$gender),]$mcs2_weight)*100, 2)
cohort_sex = as_tibble(cohort_sex) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
  add_column(Variable = c("Sex (Male)", "Sex (Female)"), .before = 1) 
  
#ethnicity
cohort_ethnicity = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$ethnicity),]$ethnicity,
                         mcs_cohort[!is.na(mcs_cohort$ethnicity),]$mcs2_weight)*100,2)
cohort_ethnicity = as_tibble(cohort_ethnicity) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("Ethnicity \n (White)",
                                   "Ethnicity \n (mixed)",
                                   "Ethnicity \n (Indian)",
                                   "Ethnicity \n (Pakistani & Bangladeshi)",
                                   "Ethnicity \n (Black/ Black British)",
                                   "Ethnicity \n (other incl. Chinese)"), .before = 1)
#EAL
cohort_eal = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$language_used_at_home),]$language_used_at_home,
                         mcs_cohort[!is.na(mcs_cohort$language_used_at_home),]$mcs2_weight)*100,2)
cohort_eal = as_tibble(cohort_eal) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("EAL \n (English only)", 
                                   "EAL \n (English and another language)",
                                   "EAL \n (only another language)"), .before = 1)

#NVQ
mcs_cohort$highest_nvq = as.factor(mcs_cohort$highest_nvq)
mcs_cohort$highest_nvq = relevel(mcs_cohort$highest_nvq, ref = "1")
cohort_nvq = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$highest_nvq),]$highest_nvq,
                         mcs_cohort[!is.na(mcs_cohort$highest_nvq),]$mcs2_weight)*100,2)
cohort_nvq =  as_tibble(cohort_nvq) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("Parent Education \n (NVQ1)",
                                   "Parent Education \n (NVQ2)",
                                   "Parent Education \n (NVQ3)",
                                   "Parent Education \n (NVQ4)", 
                                   "Parent Education \n (NVQ5)",
                                   "Parent Education \n (None of these/overseas qualifications)"), .before = 1)
#income
cohort_income = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$income_quintiles),]$income_quintiles,
                         mcs_cohort[!is.na(mcs_cohort$income_quintiles),]$mcs2_weight)*100,2)
cohort_income =  as_tibble(cohort_income) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("Income Quintile 1",
                                   "Income Quintile 2", 
                                   "Income Quintile 3", 
                                   "Income Quintile 4", 
                                   "Income Quintile 5"), .before = 1)
#occupational status
mcs_cohort$occupational_status = as.factor(mcs_cohort$occupational_status)
mcs_cohort$occupational_status = relevel(mcs_cohort$occupational_status, ref = "2")
cohort_occupation = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$occupational_status),]$occupational_status,
                         mcs_cohort[!is.na(mcs_cohort$occupational_status),]$mcs2_weight)*100,2)
cohort_occupation =  as_tibble(cohort_occupation) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("Occupational Status \n (routine)",
                                   "Occupational Status \n (intermediate)",
                                   "Occupational Status \n (higher managerial)",
                                    "Occupational Status \n (unemployed)"), .before = 1)
#imd
cohort_imd = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$imd),]$imd,
                         mcs_cohort[!is.na(mcs_cohort$imd),]$mcs2_weight)*100,2)
cohort_imd =  as_tibble(cohort_imd) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
           add_column(Variable = c("Relative Neighbourhood Deprivation \n (most deprived decile)", 
                                   "Relative Neighbourhood Deprivation \n (10 - <20%)",
                                   "Relative Neighbourhood Deprivation \n (20 - <30%)", 
                                   "Relative Neighbourhood Deprivation \n (30 - <40%)", 
                                   "Relative Neighbourhood Deprivation \n (40 - <50%)", 
                                   "Relative Neighbourhood Deprivation \n (50 - <60%)", 
                                   "Relative Neighbourhood Deprivation \n (60 - <70%)", 
                                   "Relative Neighbourhood Deprivation \n (70 - <80%)", 
                                   "Relative Neighbourhood Deprivation \n (80 - <90%)",
                                   "Relative Neighbourhood Deprivation \n (least deprived decile)"), .before = 1)

#means and SDs
#vocabulary
#Age 3
cohort_vocabAge3 = round(get_weighted_descriptives(mcs_cohort[!is.na(mcs_cohort$vocabulary_age3),]$vocabulary_age3,
                          mcs_cohort[!is.na(mcs_cohort$vocabulary_age3),]$mcs2_weight),2)
cohort_vocabAge3 = as.data.frame(t(cohort_vocabAge3)) %>% 
  rename("mean" = V1, 
         "sd" = V2, 
         "lower" = V3, 
         "upper" = V4) 
cohort_vocabAge3 = cohort_vocabAge3 %>% add_column(paste0(cohort_vocabAge3$mean,"(±",cohort_vocabAge3$sd,")", 
                                                  "\n", "[", cohort_vocabAge3$lower, ";", cohort_vocabAge3$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select(`Proportion (%) or \n Mean(±SD) [95% CIs]`) %>% 
  add_column(Variable = c("Cohort Member Vocabulary \n Age 3 (Naming Vocabulary Score)"), .before = 1)

#Age 5  
cohort_vocabAge5 = round(get_weighted_descriptives(mcs_cohort[!is.na(mcs_cohort$vocabulary_age5),]$vocabulary_age5,
                                                   mcs_cohort[!is.na(mcs_cohort$vocabulary_age5),]$mcs2_weight),2)
cohort_vocabAge5 = as.data.frame(t(cohort_vocabAge5)) %>% 
  rename("mean" = V1, 
         "sd" = V2, 
         "lower" = V3, 
         "upper" = V4) 
cohort_vocabAge5 = cohort_vocabAge5 %>% add_column(paste0(cohort_vocabAge5$mean,"(±",cohort_vocabAge5$sd,")", 
                                                          "\n", "[", cohort_vocabAge5$lower, ";", cohort_vocabAge5$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select(`Proportion (%) or \n Mean(±SD) [95% CIs]`) %>% 
  add_column(Variable = c("Cohort Member Vocabulary \n Age 5 (Naming Vocabulary Score)"), .before = 1)

#Age 11 
cohort_vocabAge11 = round(get_weighted_descriptives(mcs_cohort[!is.na(mcs_cohort$vocabulary_age11),]$vocabulary_age11,
                                                   mcs_cohort[!is.na(mcs_cohort$vocabulary_age11),]$mcs2_weight),2)
cohort_vocabAge11 = as.data.frame(t(cohort_vocabAge11)) %>% 
  rename("mean" = V1, 
         "sd" = V2, 
         "lower" = V3, 
         "upper" = V4) 
cohort_vocabAge11 = cohort_vocabAge11 %>% add_column(paste0(cohort_vocabAge11$mean,"(±",cohort_vocabAge11$sd,")", 
                                                          "\n", "[", cohort_vocabAge11$lower, ";", cohort_vocabAge11$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select(`Proportion (%) or \n Mean(±SD) [95% CIs]`) %>% 
  add_column(Variable = c("Cohort Member Vocabulary \n Age 11 (Word Similarities Score)"), .before = 1)

#Age 14
cohort_vocabAge14 = round(get_weighted_descriptives(mcs_cohort[!is.na(mcs_cohort$vocabulary_age14),]$vocabulary_age14,
                                                   mcs_cohort[!is.na(mcs_cohort$vocabulary_age14),]$mcs2_weight),2)
cohort_vocabAge14 = as.data.frame(t(cohort_vocabAge14)) %>% 
  rename("mean" = V1, 
         "sd" = V2, 
         "lower" = V3, 
         "upper" = V4) 
cohort_vocabAge14 = cohort_vocabAge14 %>% add_column(paste0(cohort_vocabAge14$mean,"(±",cohort_vocabAge14$sd,")", 
                                                          "\n", "[", cohort_vocabAge14$lower, ";", cohort_vocabAge14$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select(`Proportion (%) or \n Mean(±SD) [95% CIs]`) %>% 
  add_column(Variable = c("Cohort Member Vocabulary \n Age 14 (Word Activity Tast Score)"), .before = 1)

descriptivesCohort = rbind(cohort_vocabAge3, cohort_vocabAge5, 
                           cohort_vocabAge11, cohort_vocabAge14, 
                          cohort_sex, cohort_ethnicity, cohort_eal,
                          cohort_nvq, cohort_income, cohort_occupation, cohort_imd) %>% 
  add_row(Variable = "Vocabulary", .before = 1) %>%  #add in rows to divide table up 
  add_row(Variable = "Demographics", .before = 6) %>% 
  add_row(Variable = "Socioeconomic Circumstances", .before = 18) %>% 
  add_row(Variable = "Wealth Quintile 1", .after = 33) %>% 
  add_row(Variable = "Wealth Quintile 2", .after = 34) %>% 
  add_row(Variable = "Wealth Quintile 3", .after = 35) %>% 
  add_row(Variable = "Wealth Quintile 4", .after = 36) %>% 
  add_row(Variable = "Wealth Quintile 5", .after = 37) 
    
descriptivesCohort [is.na(descriptivesCohort )] <- " "
```

combine analytical sample and full cohort descriptives
```{r}
fullDescriptives = cbind(descriptivesCohort, descriptivesTable)
names(fullDescriptives) = c("Variable" , "Full Cohort", "Var", "Analytical Sample")
fullDescriptives = fullDescriptives %>% select(!Var)
#put into table
#define border
my_border = border= fp_border(color="black", width=1)
full_descriptives <- fullDescriptives %>% 
  flextable() %>% 
  font(fontname = "Times New Roman", part="all") %>% #
  fontsize(size=10, part = "all") %>% #
  align(j=1, align="left", part="all") %>% 
  align(j=2:3, align="center", part="all") %>% 
  color(j=1:3, color="black", part="all") %>% 
  width(j=1, width=2) %>% 
  width(j=2:3, width=1.8) %>% 
  line_spacing(j=2:3, space=1.5) %>% 
  line_spacing(j=1, space=1.5) %>% 
  border_remove() %>% 
  hline_top(j=1:3, part="all", border=my_border) %>% 
  hline_bottom(j=1:3,part="body",  border=my_border) %>% 
  bold(j = 1, i = c(1,6,18), bold = TRUE) %>% 
  italic(j = 1, i = c(1,6,18), italic = TRUE) %>% 
  set_header_labels(Variable= "Variable", `Full Cohort` = "Whole Cohort \n (N= 19243)", 
                    `Analytical Sample` = "Analytical Sample (N=17,070)") %>% 
  add_header_row(values = c(" ", "Proportion (%) or \n Mean(±SD) [95% CIs]" ), colwidths = c(1, 2)) %>% 
  font(fontname = "Times New Roman", part="header") %>% 
  align(align="center", part="header") %>% 
  hline_top(j = 2:3, part = "all", border = my_border)  %>% 
  font(fontname = "Times New Roman", part = "footer") %>% 
  fontsize(size = 9, part = "footer") %>% 
  italic(part = "footer", italic = TRUE) %>% 
  align(align="left", part="footer") %>% 
  add_header_lines(values = c("Table 2: Descriptive Statistics for Analytical Sample (N = 17, 070) and Whole MCS2001 Cohort (N=19,243)")) %>% 
  font(fontname = "Times New Roman", part = "header") %>% 
  fontsize(size = 12, part = "header") %>% 
  italic(part = "header", italic = TRUE)
  

 print(full_descriptives, preview = "docx") 
```


create flextable for descriptives
```{r}
#define border
my_border = border= fp_border(color="black", width=1)
descriptives_table <- descriptivesTable %>% 
  flextable() %>% 
  font(fontname = "Times New Roman", part="all") %>% #
  fontsize(size=10, part = "all") %>% #
  align(j=1, align="left", part="all") %>% 
  align(j=2, align="center", part="all") %>% 
  color(j=1:2, color="black", part="all") %>% 
  width(j=1, width=2) %>% 
  width(j=2, width=1.8) %>% 
  line_spacing(j=2, space=1.5) %>% 
  line_spacing(j=1, space=1.5) %>% 
  border_remove() %>% 
  hline_top(j=1:2, part="all", border=my_border) %>% 
  hline_bottom(j=1:2,part="body",  border=my_border) %>% 
  bold(j = 1, i = c(1,6,18), bold = TRUE) %>% 
  italic(j = 1, i = c(1,6,18), italic = TRUE) 
  
  
 print(descriptives_table, preview = "docx") 
```


# Language Descriptives in each SES group 

```{r}

```

