---
title: "R Notebook"
output:
  word_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

Libraries and custom functions 

```{r}

library(mice)
library(pander)
library(xtable)
library(dplyr)
library(gt)
library(glue)
library(miceadds)
library(swfscMisc)
library(imputools)
library(haven)
library(sjmisc)
library(Hmisc)
library(psych)
library(lavaan)
library(ggplot2)
library(ggpubr)
library(officer)
library(flextable)
library(ftExtra) 
library(dummies)
library(tidyverse)
library(DescTools)

weighted_descriptives_imputed_datasets<- function (dataAll,variable) {
  variable=deparse(substitute(variable))
  imputed_datasets <- unique(dataAll$.imp)
  results <- data.frame(
    Mean = as.numeric(rep(0, length(imputed_datasets))),
    SD = as.numeric(rep(0, length(imputed_datasets))),
    lower=as.numeric(rep(0, length(imputed_datasets))),
    upper=as.numeric(rep(0, length(imputed_datasets))))
  results$Imputed <-  imputed_datasets
  for (i in 1:length(imputed_datasets)) {
    data <- dataAll[dataAll$.imp == imputed_datasets[i], ]
    results[i, "Mean"] <- get_weighted_descriptives(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[1]
    results[i, "SD"] <- get_weighted_descriptives(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[2]
    results[i, "lower"] <- get_weighted_descriptives(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[3]
    results[i, "upper"] <- get_weighted_descriptives(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[4]
  }
  return (results)
}


weighted_proportions_imputed_datasets<- function (dataAll,variable) {
  variable=deparse(substitute(variable))
  imputed_datasets <- unique(dataAll$.imp)
  results <- data.frame(
    Level1 = as.numeric(rep(0, length(imputed_datasets))),
    Level2 = as.numeric(rep(0, length(imputed_datasets))),
    Level3=as.numeric(rep(0, length(imputed_datasets))),
    Level4=as.numeric(rep(0, length(imputed_datasets))),
    Level5=as.numeric(rep(0, length(imputed_datasets))),
    Level6=as.numeric(rep(0, length(imputed_datasets))),
    Level7=as.numeric(rep(0, length(imputed_datasets))),
    Level8=as.numeric(rep(0, length(imputed_datasets))),
    Level9=as.numeric(rep(0, length(imputed_datasets))),
    Level10=as.numeric(rep(0, length(imputed_datasets))))
  results$Imputed <-  imputed_datasets
  for (i in 1:length(imputed_datasets)) {
    data <- dataAll[dataAll$.imp == imputed_datasets[i], ]
    results[i, "Level1"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[1]
    results[i, "Level2"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[2]
    results[i, "Level3"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[3]
    results[i, "Level4"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[4]
    results[i, "Level5"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[5]
    results[i, "Level6"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[6]
    results[i, "Level7"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[7]
    results[i, "Level8"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[8]
    results[i, "Level9"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[9]
    results[i, "Level10"] <- get_weighted_proportions(eval(parse(text = paste("data",variable,sep="$"))), weights = data$weight)[10]
    
  }
  return (results)
}

```

Load in Data 

```{r}
load("~/Documents/updated MCS datasets/inequalities datasets /2022-10-27_mcs_ses_crossCohort/2022-10-27_mcs_ses_crossCohort.Rdata")
mcs_imputation = mi.res
load("~/Documents/updated MCS datasets/inequalities datasets /2022-10-28_bcs_ses_cross_cohort/2022-10-28_bcs_ses_cross_cohort.Rdata")
bcs_imputation = mi.res


```


Get descriptives
```{r}
#Need long datasets without original data for imputed descriptives functions 
#Rename MCS weight so that the functions will run
mcs_long = mice::complete(mcs_imputation, "long", include=FALSE)
mcs_long$weight = mcs_long$weight2

bcs_long = mice::complete(bcs_imputation, "long", include=FALSE)

#bcs analysis data ####

#Vocabulary ####
age5_vocabBCS = weighted_descriptives_imputed_datasets(bcs_long, age5_vocab)
age10_vocabBCS = weighted_descriptives_imputed_datasets(bcs_long, age10_vocab)
age16_vocabBCS = weighted_descriptives_imputed_datasets(bcs_long, age16_vocab)


combined_vocab_age5DescriptivesBCS = round(combine_imputed_descriptives(age5_vocabBCS),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1) 

combined_vocab_age10DescriptivesBCS = round(combine_imputed_descriptives(age10_vocabBCS),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1) 

combined_vocab_age16DescriptivesBCS = round(combine_imputed_descriptives(age16_vocabBCS),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1) 


#proportions

sexProportionsBCS = weighted_proportions_imputed_datasets(bcs_long, sex) %>% 
  select(Level1:Level2) 
ethnicityProportionsBCS = weighted_proportions_imputed_datasets(bcs_long, ethnicity) %>% 
  select(Level1:Level2) 
ealProportionsBCS = weighted_proportions_imputed_datasets(bcs_long, EAL) %>% 
  select(Level1:Level2) 
educationProportionsBCS = weighted_proportions_imputed_datasets(bcs_long, highestEd1) %>% 
  select(Level1:Level4) 
incomeProportionsBCS = weighted_proportions_imputed_datasets(bcs_long, oecd_quintiles) %>% 
  select(Level1:Level5) 
occupationProportionsBCS = weighted_proportions_imputed_datasets(bcs_long, occupational_status) %>% 
  select(Level1:Level5) 


sexCombinedBCS = round(combine_imputed_descriptives(sexProportionsBCS)*100, 2) %>% 
  slice_head(n=1) %>% 
  rename("Sex (Male)" = Level1,
         "Sex (Female)" = Level2) 
sexCombinedBCS = as.data.frame(t(sexCombinedBCS)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
ethnicityCombinedBCS = round(combine_imputed_descriptives(ethnicityProportionsBCS)*100,2)%>% 
  slice_head(n=1) %>% 
  rename( "Ethnicity \n (White)" = Level1, 
          "Ethnicity \n (Minority)" = Level2)
ethnicityCombinedBCS = as.data.frame(t(ethnicityCombinedBCS)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
ealCombinedBCS = round(combine_imputed_descriptives(ealProportionsBCS)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("EAL \n (English only)" = Level1, 
         "EAL \n (EAL)" = Level2)
ealCombinedBCS = as.data.frame(t(ealCombinedBCS)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
educationCombinedBCS = round(combine_imputed_descriptives(educationProportionsBCS)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Parent education \n (no/low level)" = Level1, 
         "Parent Education \n (O-levels/GCSEs grades A*-C)"= Level2, 
         "Parent Education \n (post-16 quals)" = Level3,
         "Parent Education \n (university level quals)" = Level4)
educationCombinedBCS = as.data.frame(t(educationCombinedBCS)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
incomeCombinedBCS = round(combine_imputed_descriptives(incomeProportionsBCS)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Income Quintile 1" = Level1, 
         "Income Quintile 2" = Level2, 
         "Income Quintile 3" = Level3, 
         "Income Quintile 4" = Level4 , 
         "Income Quintile 5" = Level5)
incomeCombined = as.data.frame(t(incomeCombinedBCS)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
occupationCombinedBCS = round(combine_imputed_descriptives(occupationProportionsBCS)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Occupational Status \n (routine)" = Level1, 
         "Occupational Status \n (intermediate)" = Level2,
         "Occupational Status \n (higher managerial)" = Level3,
         "Occupational Status \n (unemployed)" = Level4)
occupationCombinedBCS = as.data.frame(t(occupationCombinedBCS)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 

BCSdescriptivesTable = rbind(combined_vocab_age5DescriptivesBCS,
                          combined_vocab_age10DescriptivesBCS, combined_vocab_age5DescriptivesBCS,
                          sexCombinedBCS, ethnicityCombinedBCS, ealCombinedBCS, 
                          educationCombinedBCS, incomeCombinedBCS,  occupationCombinedBCS) %>% 
  add_row(Variable = "Vocabulary", .before = 1) %>%  #add in rows to divide table up 
  add_row(Variable = "Demographics", .before = 4) %>% #needs fixing
  add_row(Variable = "Socioeconomic Circumstances", .before = 12)
BCSdescriptivesTable [is.na(BCSdescriptivesTable )] <- " "

#mcs analysis data  ####

#Vocabulary ####
age5_vocabMCS = weighted_descriptives_imputed_datasets(mcs_long, age5_vocab)
age11_vocabMCS = weighted_descriptives_imputed_datasets(mcs_long, age11_vocab)
age14_vocabMCS = weighted_descriptives_imputed_datasets(mcs_long, age14_vocab)


combined_vocab_age5DescriptivesMCS = round(combine_imputed_descriptives(age5_vocabMCS),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1) 

combined_vocab_age11DescriptivesMCS = round(combine_imputed_descriptives(age11_vocabMCS),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1) 

combined_vocab_age14DescriptivesMCS = round(combine_imputed_descriptives(age14_vocabMCS),2) %>% 
  select(!Imputed) %>% 
  slice_head(n=1) 

#proportions

sexProportionsMCS = weighted_proportions_imputed_datasets(mcs_long, sex) %>% 
  select(Level1:Level2) 
ethnicityProportionsMCS = weighted_proportions_imputed_datasets(mcs_long, ethnicity) %>% 
  select(Level1:Level2) 
ealProportionsMCS = weighted_proportions_imputed_datasets(mcs_long, EAL) %>% 
  select(Level1:Level2) 
educationProportionsMCS = weighted_proportions_imputed_datasets(mcs_long, highested1) %>% 
  select(Level1:Level4) 
incomeProportionsMCS = weighted_proportions_imputed_datasets(mcs_long, income_quintiles) %>% 
  select(Level1:Level5) 
occupationProportionsMCS = weighted_proportions_imputed_datasets(mcs_long, occupational_status) %>% 
  select(Level1:Level4) 


sexCombinedMCS = round(combine_imputed_descriptives(sexProportionsMCS)*100, 2) %>% 
  slice_head(n=1) %>% 
  rename("Sex (Male)" = Level1,
         "Sex (Female)" = Level2) 
sexCombinedMCS = as.data.frame(t(sexCombinedMCS)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
ethnicityCombinedMCS = round(combine_imputed_descriptives(ethnicityProportionsMCS)*100,2)%>% 
  slice_head(n=1) %>% 
  rename( "Ethnicity \n (White)" = Level1, 
          "Ethnicity \n (Minority)" = Level2)
ethnicityCombinedMCS = as.data.frame(t(ethnicityCombinedMCS)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
ealCombinedMCS = round(combine_imputed_descriptives(ealProportionsMCS)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("EAL \n (English only)" = Level1, 
         "EAL \n (EAL)" = Level2)
ealCombinedMCS = as.data.frame(t(ealCombinedMCS)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
educationCombinedMCS = round(combine_imputed_descriptives(educationProportionsMCS)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Parent education \n (no/low level)" = Level1, 
         "Parent Education \n (O-levels/GCSEs grades A*-C)"= Level2, 
         "Parent Education \n (post-16 quals)" = Level3,
         "Parent Education \n (university level quals)" = Level4)
educationCombinedMCS = as.data.frame(t(educationCombinedMCS)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
incomeCombinedMCS = round(combine_imputed_descriptives(incomeProportionsMCS)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Income Quintile 1" = Level1, 
         "Income Quintile 2" = Level2, 
         "Income Quintile 3" = Level3, 
         "Income Quintile 4" = Level4 , 
         "Income Quintile 5" = Level5)
incomeCombined = as.data.frame(t(incomeCombinedMCS)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 
occupationCombinedMCS = round(combine_imputed_descriptives(occupationProportionsMCS)*100,2)%>% 
  slice_head(n=1) %>% 
  rename("Occupational Status \n (routine)" = Level1, 
         "Occupational Status \n (intermediate)" = Level2,
         "Occupational Status \n (higher managerial)" = Level3,
         "Occupational Status \n (unemployed)" = Level4)
occupationCombinedMCS = as.data.frame(t(occupationCombinedMCS)) %>% 
  rownames_to_column() %>% 
  rename("Variable" = rowname,
         "Proportion (%) or \n Mean(±SD) [95% CIs]" = V1) 


MCSdescriptivesTable = rbind(vocabulary_age5DescriptivesMCS,
                          vocabulary_age11DescriptivesMCS, vocabulary_age14DescriptivesMCS,
                          sexCombinedMCS, ethnicityCombinedMCS, ealCombinedMCS, 
                          educationCombinedMCS, incomeCombinedMCS,  occupationCombinedMCS) %>% 
  add_row(Variable = "Vocabulary", .before = 1) %>%  #add in rows to divide table up 
  add_row(Variable = "Demographics", .before = 4) %>% 
  add_row(Variable = "Socioeconomic Circumstances", .before = 12)
MCSdescriptivesTable [is.na(MCSdescriptivesTable )] <- " "



```

Whole Cohort Descriptives 

```{r}

#read in full cohort data
#MCS ####

mcs_cohort<-read.csv("mcs_ses_comparison_data.csv")
mcs_cohort[,1]<- NULL
#redorder nvq and occupational status variables 

#get weighted proportions - need to remove NA values 
#sex
MCScohort_sex = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$sex),]$sex,
                                            mcs_cohort[!is.na(mcs_cohort$sex),]$weight2)*100, 2)
MCScohort_sex = as_tibble(MCScohort_sex) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
  add_column(Variable = c("Sex (Male)", "Sex (Female)"), .before = 1) 

#ethnicity
MCScohort_ethnicity = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$ethnicity),]$ethnicity,
                                                  mcs_cohort[!is.na(mcs_cohort$ethnicity),]$weight2)*100,2)
MCScohort_ethnicity = as_tibble(MCScohort_ethnicity) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
  add_column(Variable = c("Ethnicity \n (White)",
                          "Ethnicity \n (Minority)"), .before = 1)
#EAL
MCScohort_eal = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$EAL),]$EAL,
                                            mcs_cohort[!is.na(mcs_cohort$EAL),]$weight2)*100,2)
MCScohort_eal = as_tibble(MCScohort_eal) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
  add_column(Variable = c("EAL \n (English only)", 
                          "EAL \n (EAL)"), .before = 1)

#NVQ
mcs_cohort$highest_nvq = as.factor(mcs_cohort$highested1)
MCScohort_nvq = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$highested1),]$highested1,
                                            mcs_cohort[!is.na(mcs_cohort$highested1),]$weight2)*100,2)
MCScohort_nvq =  as_tibble(MCScohort_nvq) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
  add_column(Variable = c("Parent Education \n (no/low level)",
                          "Parent Education \n (O-levels/GCSEs grades A*-C)",
                          "Parent Education \n (post-16 quals)",
                          "Parent Education \n (university level quals)"), .before = 1)
#income
MCScohort_income = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$income_quintiles),]$income_quintiles,
                                               mcs_cohort[!is.na(mcs_cohort$income_quintiles),]$weight2)*100,2)
MCScohort_income =  as_tibble(MCScohort_income) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
  add_column(Variable = c("Income Quintile 1",
                          "Income Quintile 2", 
                          "Income Quintile 3", 
                          "Income Quintile 4", 
                          "Income Quintile 5"), .before = 1)
#occupational status
mcs_cohort$occupational_status = as.factor(mcs_cohort$occupational_status)
MCScohort_occupation = round(get_weighted_proportions(mcs_cohort[!is.na(mcs_cohort$occupational_status),]$occupational_status,
                                                   mcs_cohort[!is.na(mcs_cohort$occupational_status),]$weight2)*100,2)
MCScohort_occupation =  as_tibble(MCScohort_occupation) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = value) %>% 
  add_column(Variable = c("Occupational Status \n (routine)", #check ordering of this
                          "Occupational Status \n (intermediate)",
                          "Occupational Status \n (higher managerial)",
                          "Occupational Status \n (unemployed)"), .before = 1)

#means and SDs
#vocabulary

#Age 5  
MCScohort_vocabAge5 = round(get_weighted_descriptives(mcs_cohort[!is.na(mcs_cohort$age5_vocab),]$age5_vocab,
                                                   mcs_cohort[!is.na(mcs_cohort$age5_vocab),]$weight2),2)
MCScohort_vocabAge5 = as.data.frame(t(MCScohort_vocabAge5)) %>% 
  rename("mean" = V1, 
         "sd" = V2, 
         "lower" = V3, 
         "upper" = V4) 
MCScohort_vocabAge5 = MCScohort_vocabAge5 %>% add_column(paste0(MCScohort_vocabAge5$mean,"(±",MCScohort_vocabAge5$sd,")", 
                                                          "\n", "[", MCScohort_vocabAge5$lower, ";", MCScohort_vocabAge5$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select(`Proportion (%) or \n Mean(±SD) [95% CIs]`) %>% 
  add_column(Variable = c("Cohort Member Vocabulary \n Age 5 (Naming Vocabulary Score)"), .before = 1)

#Age 11 
MCScohort_vocabAge11 = round(get_weighted_descriptives(mcs_cohort[!is.na(mcs_cohort$age11_vocab),]$age11_vocab,
                                                    mcs_cohort[!is.na(mcs_cohort$age11_vocab),]$weight2),2)
MCScohort_vocabAge11 = as.data.frame(t(MCScohort_vocabAge11)) %>% 
  rename("mean" = V1, 
         "sd" = V2, 
         "lower" = V3, 
         "upper" = V4) 
MCScohort_vocabAge11 = MCScohort_vocabAge11 %>% add_column(paste0(MCScohort_vocabAge11$mean,"(±",MCScohort_vocabAge11$sd,")", 
                                                            "\n", "[", MCScohort_vocabAge11$lower, ";", MCScohort_vocabAge11$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select(`Proportion (%) or \n Mean(±SD) [95% CIs]`) %>% 
  add_column(Variable = c("Cohort Member Vocabulary \n Age 11 (Word Similarities Score)"), .before = 1)

#Age 14
MCScohort_vocabAge14 = round(get_weighted_descriptives(mcs_cohort[!is.na(mcs_cohort$age14_vocab),]$age14_vocab,
                                                    mcs_cohort[!is.na(mcs_cohort$age14_vocab),]$weight2),2)
MCScohort_vocabAge14 = as.data.frame(t(MCScohort_vocabAge14)) %>% 
  rename("mean" = V1, 
         "sd" = V2, 
         "lower" = V3, 
         "upper" = V4) 
MCScohort_vocabAge14 = MCScohort_vocabAge14 %>% add_column(paste0(MCScohort_vocabAge14$mean,"(±",MCScohort_vocabAge14$sd,")", 
                                                            "\n", "[", MCScohort_vocabAge14$lower, ";", MCScohort_vocabAge14$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select("Proportion (%) or \n Mean(±SD) [95% CIs]") %>% 
  add_column(Variable = c("Cohort Member Vocabulary \n Age 14 (Word Activity Tast Score)"), .before = 1)

descriptivesCohortMCS = rbind(MCScohort_vocabAge5, 
MCScohort_vocabAge11, MCScohort_vocabAge14, 
MCScohort_sex, MCScohort_ethnicity, MCScohort_eal,
MCScohort_nvq, MCScohort_income, MCScohort_occupation) %>% 

  add_row(Variable = "Vocabulary", .before = 1) %>%  #add in rows to divide table up 
  add_row(Variable = "Demographics", .before = 4) %>% 
  add_row(Variable = "Socioeconomic Circumstances", .before = 12)
    
descriptivesCohortMCS [is.na(descriptivesCohortMCS )] <- " "

#bcs cohort ####

bcs_cohort<-read.csv("bcs_ses_comparison_data.csv")
bcs_cohort[,1]<- NULL

#means and SDs
#vocabulary

#Age 5  
BCScohort_vocabAge5 = round(MeanCI(bcs_cohort$age5_vocab, na.rm = TRUE),2)
BCScohort_vocabAge5 = as.data.frame(t(BCScohort_vocabAge5)) %>% 
  rename("lower" = lwr.ci, 
         "upper" = upr.ci) %>% 
  mutate(sd = round(sd(bcs_cohort$age5_vocab, na.rm = TRUE),2), .after = 1)
BCScohort_vocabAge5 = BCScohort_vocabAge5 %>% add_column(paste0(BCScohort_vocabAge5$mean,"(±",BCScohort_vocabAge5$sd,")", 
                                                                "\n", "[", BCScohort_vocabAge5$lower, ";", BCScohort_vocabAge5$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select(`Proportion (%) or \n Mean(±SD) [95% CIs]`) %>% 
  add_column(Variable = c("Cohort Member Vocabulary \n Age 5 (EPVT)"), .before = 1)

#Age 10
BCScohort_vocabAge10 = round(MeanCI(bcs_cohort$b10bass, na.rm = TRUE),2)
BCScohort_vocabAge10 = as.data.frame(t(BCScohort_vocabAge10)) %>% 
  rename("lower" = lwr.ci, 
         "upper" = upr.ci) %>% 
  mutate(sd = round(sd(bcs_cohort$b10bass, na.rm = TRUE),2), .after = 1)
BCScohort_vocabAge10 = BCScohort_vocabAge10 %>% add_column(paste0(BCScohort_vocabAge10$mean,"(±",BCScohort_vocabAge10$sd,")", 
                                                                  "\n", "[", BCScohort_vocabAge10$lower, ";", BCScohort_vocabAge10$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select(`Proportion (%) or \n Mean(±SD) [95% CIs]`) %>% 
  add_column(Variable = c("Cohort Member Vocabulary \n Age 10 (Verbal Similarities Score)"), .before = 1)

#Age 16
BCScohort_vocabAge16 = round(MeanCI(bcs_cohort$b16vocab, na.rm = TRUE),2)
BCScohort_vocabAge16 = as.data.frame(t(BCScohort_vocabAge16)) %>% 
  rename("lower" = lwr.ci, 
         "upper" = upr.ci) %>% 
  mutate(sd = round(sd(bcs_cohort$b16vocab, na.rm = TRUE),2), .after = 1)
BCScohort_vocabAge16 = BCScohort_vocabAge16 %>% add_column(paste0(BCScohort_vocabAge16$mean,"(±",BCScohort_vocabAge16$sd,")", 
                                                                  "\n", "[", BCScohort_vocabAge16$lower, ";", BCScohort_vocabAge16$upper,"]")) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = `paste0(...)`) %>% 
  select(`Proportion (%) or \n Mean(±SD) [95% CIs]`) %>% 
  add_column(Variable = c("Cohort Member Vocabulary \n Age 16 (Vocabulary Test)"), .before = 1)

#Proportions ####
#sex
BCSgender = bcs_cohort %>% select(bcsid, a0255)
BCSgender = na.omit(BCSgender)
BCSgender$a0255 = as.factor(BCSgender$a0255)
BCSsex = table(BCSgender$a0255)
BCScohort_sex = as.data.frame(round(prop.table(sex),4)*100)
  
BCScohort_sex = as_tibble(BCScohort_sex) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = Freq) %>% 
  add_column(Variable = c("Sex (Male)", "Sex (Female)"), .before = 1)  %>% 
  select(-Var1)

#Ethnicity 

BCSethnicity = bcs_cohort %>% select(bcsid, ethnicity )
BCSethnicity = na.omit(BCSethnicity)
BCSethnicity$ethnicity = as.factor(BCSethnicity$ethnicity)
BCSethnicity = table(BCSethnicity$ethnicity)
BCScohort_ethnicity = as.data.frame(round(prop.table(BCSethnicity),4)*100)

BCScohort_ethnicity = as_tibble(BCScohort_ethnicity) %>% 
  rename("Proportion (%) or \n Mean(±SD) [95% CIs]" = Freq) %>% 
  add_column(Variable = c("Ethnicity (White)", "Ethnicity (Minority)"), .before = 1)  %>% 
  select(-Var1)



```










#whole cohorts
bcs_cohort<-read.csv("bcs_whole_cohort.csv")
bcs_cohort[,8]<- NULL
bcs_cohort[,8]<- NULL

names(bcs_cohort) <- c("id", "gender", "ethnicity", "EAL", "mothers_age", "accommodation_type",  
                     "highest_household_education",  "occupational_status", "age5_vocab", "age_5" ,
                     "age10_vocab","age10", "age16_vocab", "age16")

#not weighted here as it is just the attrition weight that we have for BCS, not sample weight. 
vocab= bcs_cohort %>% select(id, age5_vocab, age10_vocab, age16_vocab)
describe(vocab)

round(MeanCI(vocab$age5_vocab, na.rm = TRUE),2)
round(MeanCI(vocab$age10_vocab, na.rm = TRUE),2)
round(MeanCI(vocab$age16_vocab, na.rm = TRUE),2)

#proportions

gender = bcs_cohort %>% select(id, gender)
gender = na.omit(gender)
gender$gender = as.factor(gender$gender)
sex = table(gender$gender)
round(prop.table(sex),4)*100


ethnicity = bcs_cohort %>% select(id, ethnicity)
ethnicity = na.omit(ethnicity)
ethnicity$ethnicity = as.factor(ethnicity$eethnicity)
ethnic = table(ethnicity$ethnicity)
round(prop.table(ethnic),4)*100


EAL = bcs_cohort %>% select(id, EAL)
EAL = na.omit(EAL)
EAL$EAL = as.factor(EAL$eEAL)
lang = table(EAL$EAL)
round(prop.table(lang),4)*100

highest_household_education = bcs_cohort %>% select(id, highest_household_education)
highest_household_education = na.omit(highest_household_education)
highest_household_education$highest_household_education = as.factor(highest_household_education$ehighest_household_education)
education = table(highest_household_education$highest_household_education)
round(prop.table(education),4)*100

occupational_status = bcs_cohort %>% select(id, occupational_status)
occupational_status = na.omit(occupational_status)
occupational_status$occupational_status = as.factor(occupational_status$occupational_status)
occupation = table(occupational_status$occupational_status)
round(prop.table(occupation),4)*100


#MCS whole cohort. 
mcs_cohort<-read.csv("mcs_crossCohort_fullCohort.csv")
mcs_cohort[,1]<- NULL

names(mcs_cohort) <- c("id", "gender", "ethnicity", "EAL", "mothers_age", "accommodation_type",  
                       "highest_household_education",  "occupational_status", "age5_vocab", "age_5" ,
                       "age11_vocab","age11", "age14_vocab", "age14", "weight")


age5_vocab = mcs_cohort %>% select(id, age5_vocab, weight)
vocab_age5=na.omit(age5_vocab)
round(get_weighted_descriptives(vocab_age5$age5_vocab, vocab_age5$weight),2)

age11_vocab = mcs_cohort %>% select(id, age11_vocab, weight)
vocab_age11=na.omit(age11_vocab)
round(get_weighted_descriptives(vocab_age11$age11_vocab, vocab_age11$weight),2)

age14_vocab = mcs_cohort %>% select(id, age14_vocab, weight)
vocab_age14=na.omit(age14_vocab)
round(get_weighted_descriptives(vocab_age14$age14_vocab, vocab_age14$weight),2)

#proportions

gender = mcs_cohort %>% select(id, gender, weight)
gender = na.omit(gender)
round(get_weighted_proportions(gender$gender, gender$weight), 4)*100

ethnicity = mcs_cohort %>% select(id, ethnicity, weight)
ethnicity = na.omit(ethnicity)
round(get_weighted_proportions(ethnicity$ethnicity, ethnicity$weight), 4)*100

EAL = mcs_cohort %>% select(id, EAL, weight)
EAL = na.omit(EAL)
round(get_weighted_proportions(EAL$EAL, EAL$weight), 4)*100

highest_household_education = mcs_cohort %>% select(id, highest_household_education, weight)
highest_household_education = na.omit(highest_household_education)
round(get_weighted_proportions(highest_household_education$highest_household_education, highest_household_education$weight), 4)*100




occupational_status = mcs_cohort %>% select(id, occupational_status, weight)
occupational_status = na.omit(occupational_status)
round(get_weighted_proportions(occupational_status$occupational_status, occupational_status$weight), 4)*100




